Board games group recomendation using metadata

### 2024-12-09 paper v2/paper v2.tex
feat: future work

@@

To evaluate the results of our model, we will compare it to most popular as a sanity check, to iknn applied to the same dataset and to SVD applied to the same dataset. % Agregar AGREE si logramos hacerlo funcionar ahora que tenemos menos datos.

@@

\begin{itemize}
    \item Precision at k: This metric measures the proportion of recommended items that are relevant to the user, where relevance is defined as the items that the user has interacted with.
    \item Recall at k: This metric measures the proportion of relevant items that are recommended to the user.
    \item nDCG@k: This metric measures the normalized discounted cumulative gain at k, and is used to measure the quality of the recommendations.
    \item Relevance Score: This metric evaluates how relevant the recommendations are to the user, providing an indication of the recommendation quality.
    \item Diversity: This metric assesses the variety of the recommendations, ensuring a wide range of different items are suggested.
    \item Novelty: This metric measures how new or unexpected the recommendations are to the user, contributing to the overall recommendation quality.
    \item Fairness: This metric evaluates the fairness of the recommendations, ensuring that the recommendations are unbiased and equitable.
    \item Serendipity: This metric measures the likelihood of the recommendations to pleasantly surprise the user, enhancing the user experience.
\end{itemize}

@@

\newline
One aspect of the recommendations that is worth mentioning is that the LightFM model is capable of superior results with more diversity. This means that all groups will get recommended different games, but they are tailored to the preferences of each user on a group. This in hand increases the novelty and the serendipity of the recommendations, creating more unique experiences for the users.

\newline
For each different group formation, the results are the same. This is to be expected, since the group formation is based on the preferences of the users, and the recommendations are made based on the preferences of the group. Not on the preferences of the individual users. This is a good sign, beacuase it shows that the model does not overfit to any group formation and it is able to make recommendations based on the preferences of the group.

\newline

However, for new users, the results might not be as expected. The user needs to create user-item interactions in order to get proper recommendations.
\begin{table}[]
    \centering
    \begin{tabular}{|l|l|l|l|}
        \hline
        \textbf{Statistic} & \textbf{LightFM} & \textbf{SVD} & \textbf{Most Popular} \\ \hline
        Precision          & 0.3660           & 0.2020       & 0.3010                \\
        Recall@5           & 0.0942           & 0.0520       & 0.0766                \\
        nDCG@5             & 0.6232           & 0.4762       & 0.5903                \\
        Relevance Score    & 2.76             & 1.59         & 2.32                  \\
        Diversity          & 0.03             & 0.01         & 0.01                  \\
        Novelty            & 5.89             & 8.52         & 5.70                  \\
        Fairness           & 0.60             & 0.72         & 0.66                  \\
        Serendipity        & 4.51             & 2.80         & 3.63                  \\ \hline
    \end{tabular}
    \caption{Random groups recomendation results}
    \label{tab:resultados-modelos}
\end{table}

\begin{table}[]
    \centering
    \begin{tabular}{|l|l|l|l|}
        \hline
        \textbf{Statistic} & \textbf{LightFM} & \textbf{SVD} & \textbf{Most Popular} \\ \hline
        Precision          & 0.3350           & 0.2040       & 0.3240                \\
        Recall@5           & 0.0821           & 0.0498       & 0.0749                \\
        nDCG@5             & 0.5722           & 0.4736       & 0.5474                \\
        Relevance Score    & 2.57             & 1.62         & 2.48                  \\
        Diversity          & 0.04             & 0.01         & 0.01                  \\
        Novelty            & 5.99             & 8.60         & 5.70                  \\
        Fairness           & 0.63             & 0.72         & 0.64                  \\
        Serendipity        & 4.61             & 2.75         & 4.06                  \\ \hline
    \end{tabular}
    \caption{Similar groups recommendation results}
    \label{tab:resultados-modelos-similar}
\end{table}

@@

>>>>

For this project we will use the LightFM library\footnote{\cite{DBLP:conf/recsys/Kula15}} to make the recommendations, which is a Python implementation of a factorization machine for collaborative filtering.

We will also use SVD models from the scikit-learn library\footnote{\cite{scikit-learn}} to compare the results of our model with a more traditional approach, and the most popular model as a baseline. SVD was selected above other models like k-nearest due to its usage as industry standard\footnote{\cite{Roy2022}} and due to taking less time executing.

@@

To evaluate the results of our model, we will compare it to most popular as a sanity check and to SVD applied to the same dataset and groups. % Agregar AGREE si logramos hacerlo funcionar ahora que tenemos menos datos.

@@

\begin{itemize}
    \item Precision@k: This metric measures the proportion of recommended items that are relevant to the user, where relevance is defined as the items that the user has interacted with.
    \item Recall@k: This metric measures the proportion of relevant items that are recommended to the user.
    \item nDCG@k: This metric measures the normalized discounted cumulative gain at k, and is used to measure the quality of the recommendations.
    \item Relevance Score: This metric evaluates how relevant the recommendations are to the user, providing an indication of the recommendation quality.
    \item Diversity: This metric assesses the variety of the recommendations, ensuring a wide range of different items are suggested.
    \item Novelty: This metric measures how new or unexpected the recommendations are to the user, contributing to the overall recommendation quality.
    \item Fairness: This metric evaluates the fairness of the recommendations, ensuring that the recommendations are unbiased and equitable.
    \item Serendipity: This metric measures the likelihood of the recommendations to pleasantly surprise the user, enhancing the user experience.
\end{itemize}

@@

One aspect of the recommendations that is worth mentioning is that the LightFM model is capable of superior results with more diversity. This means that all groups will get recommended different games, but they are tailored to the preferences of each user on a group. This in hand increases the novelty and the serendipity of the recommendations, creating more unique experiences for the users.

For each different group formation, the results are mostly the same. This is to be expected, since the group formation is based on the preferences of the users, and the recommendations are made based on the preferences of the group. Not on the preferences of the individual users. This is a good sign, beacuase it shows that the model does not overfit to any group formation and it is able to make recommendations based on the preferences of the group.

However, for new users, the results might not be as expected. The user needs to create user-item interactions in order to get proper recommendations. Untill then, the model should be able to recommend the most popular items, which are the most likely to be relevant to the user according to the very low information the model has.

\begin{table}[]
    \centering
    \begin{tabular}{|l|l|l|l|}
        \hline
        \textbf{Statistic} & \textbf{LightFM} & \textbf{SVD} & \textbf{Most Popular} \\ \hline
        Precision@5        & 0.3660           & 0.2020       & 0.3010                \\
        Recall@5           & 0.0942           & 0.0520       & 0.0766                \\
        nDCG@5             & 0.6232           & 0.4762       & 0.5903                \\
        Relevance Score    & 2.76             & 1.59         & 2.32                  \\
        Diversity          & 0.03             & 0.01         & 0.01                  \\
        Novelty            & 5.89             & 8.52         & 5.70                  \\
        Fairness           & 0.60             & 0.72         & 0.66                  \\
        Serendipity        & 4.51             & 2.80         & 3.63                  \\ \hline
    \end{tabular}
    \caption{Random groups recomendation results}
    \label{tab:resultados-modelos}
\end{table}

\begin{table}[]
    \centering
    \begin{tabular}{|l|l|l|l|}
        \hline
        \textbf{Statistic} & \textbf{LightFM} & \textbf{SVD} & \textbf{Most Popular} \\ \hline
        Precision@5        & 0.3350           & 0.2040       & 0.3240                \\
        Recall@5           & 0.0821           & 0.0498       & 0.0749                \\
        nDCG@5             & 0.5722           & 0.4736       & 0.5474                \\
        Relevance Score    & 2.57             & 1.62         & 2.48                  \\
        Diversity          & 0.04             & 0.01         & 0.01                  \\
        Novelty            & 5.99             & 8.60         & 5.70                  \\
        Fairness           & 0.63             & 0.72         & 0.64                  \\
        Serendipity        & 4.61             & 2.75         & 4.06                  \\ \hline
    \end{tabular}
    \caption{Similar groups recommendation results}
    \label{tab:resultados-modelos-similar}
\end{table}

@@

\section{Future work}

Since this project was done with a reduced dataset, the obvious step would be to scale it up to the full dataset or at least a bigger portion of it with improved computation power. This would allow for more accurate results and a more robust set of models.

Another step would be to improve the group formation algorithm, as it is currently based on the preferences of the users, and not on the characteristics of the games they play (it does not use the available metadata). This could be done by using a clustering algorithm to group the games based on their characteristics, and then grouping the users based on the games they have interacted with. Future work could also use a hybrid approach, where part of how the groups are formed is random and another part is based on the similarity of the users.

Additionally, a notable drawback of this work is the lack of inclusion of the baseline "AGREE" recommended by the course instructors of IIC3633. Since the dataset selection process was finalized late in the development of this work, this implementation was not completed.

Finally, there is exploration to do regarding the use of the least misery and dictatorship aggregation functions, as well as the use of other aggregation functions that could be more suitable for group recommendations. This could be done by comparing the results of the different aggregation functions and selecting the one that provides the best recommendations. This barely didnt make it into the project, and could easily be implemented in the future.
